Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.qmd
change decomposition caption

Illustration of how analysing a system with Maud can yield actionable insights
about the underlying metabolic network.  (**Top Left**) A schematic of the
regulatory interactions associated with the enzyme $GNMT1$. Dashed green
lines represents allosteric activation, dashed red lines indicate allosteric
inhibition and solid red lines represent competitive inhibition. (**Bottom
Left**) Comparison of marginal posterior distributions for $GNMT$ flux in
conditions 1 and 2. (**Right**) Log-scale ratios of the regulatory elements
defined in equation \eqref{eq-decomposition}. Note that the $Reversibility$
and $k_cat$ components are excluded: this is because this reaction was modelled
as irreversible, and $k_{cat}$ was modelled as constant across conditions.
These plots identify why flux in condition 2 is higher than in condition 1: the
flux increase is due to allostery and saturation with no control from enzyme
concentration changes.

>>>>

Illustration of how analysing a system with Maud can yield actionable insights
about the underlying metabolic network.  (**Top Left**) A schematic of the
regulatory interactions associated with the enzyme $GNMT1$. Dashed green
lines represents allosteric activation, dashed red lines indicate allosteric
inhibition and solid red lines represent competitive inhibition. (**Bottom
Left**) Comparison of marginal posterior distributions for $GNMT$ flux in
datasets 1 and 2. (**Right**) Log-scale ratios of the regulatory elements
defined in equation \eqref{eq-decomposition}. Note that the $Reversibility$
and $k_cat$ components are excluded: this is because this reaction was modelled
as irreversible, and $k_{cat}$ was modelled as constant across datasets.
These plots identify why flux in dataset 12 is higher than in dataset 1: the
flux increase is due to allostery and saturation with no control from enzyme
concentration changes.
